Enhancing \Hinf{} Norm Estimation using Local LPM/LRM Modeling: Applied to an AVIS\thanksref{thx}

### 2016-07-15 ch02-qlogms/excitation-design.tex
Some clarifications on notation

  We then calculate the theoretical variance on the magnitude of the peak in the \gls{FRF} ($\abs{ G\left( \wM \right) }$) as shown in \eqref{eq:excitation:varPeak} for a coarse grid.
  %TODO: clarify previous sentence
  A coarse grid was chosen with $\tilde{\alpha} = 10$; this means that the spacing between the excited lines around the resonance are much larger than the system bandwidth.
  It is obvious that such an excitation signal will not perform well in most cases, as the resonance peak is very likely to be overlooked in such an \gls{FRF}.

>>>>

  We then calculate the theoretical variance on the magnitude of the peak in the \gls{FRF} ($\abs{ G\left( \wM \right) }$), as shown in \eqref{eq:excitation:varPeak}, for a coarse grid.
  A coarse grid was chosen with $\tilde{\alpha} = 10$; this means that the spacing between the excited lines around the resonance are much larger than the system bandwidth.
  It is obvious that such an excitation signal will not perform well in most cases, as the resonance peak is very likely to be overlooked in such an \gls{FRF}.

### 2016-07-15 ch04-lrmhinf/lrmhinf.tex
Some clarifications on notation

\paragraph{Interpolation method}
To allow inspection of $\svdMax{\Delta(\omega)}$ in~\eqref{eq:lrmhinf:HinfNormSISO} for arbitrary values of $\omega \in \Omega$, we propose an interpolation approach to estimate $\gamma$ and to allow visual inspection of $\svdMax{\Delta(\omega)}$.
It can be understood intuitively that due to the limited validity domain of the local models, an estimate of $\Delta(\omega)$ can only be obtained from $\LocalModel[k(\omega)]{\Delta}$ when the distance $\abs{\omega_k-\omega}$ is small.
As the local models are each constructed around the frequency $\omega_k$, for an arbitrary $\omega \in \Omega$, one can find two adjacent frequencies around which such local models are available.
To this end, two functions that indicate respectively the left and the right adjacent local models for frequency $\omega \in \Omega$ are defined:
\begin{align}
  \leftAdjacent(\omega) & 
                \isdef
                  \max
                  \Set{
                    k 
                    |
                      \omega_k \in \DFTGrid,  \omega_k \leq \omega
                  }\\
  \rightAdjacent(\omega) & 
                \isdef
                  \min
                  \Set{
                    k
                    |
                      \omega_k \in \DFTGrid,  \omega_k \geq \omega
                  }
  \text{.}
  \label{eq:lrmhinf:kL-kR-indexing-functions}
\end{align}
Using the $\leftAdjacent(\omega)$ and $\rightAdjacent(\omega)$ functions, two candidate values for $\svdMax{\Delta(\omega)}$ are obtained:
\begin{equation*}
 \svdMax{\LocalModel[\leftAdjacent(\omega)]{\Delta}(\omega)} 
 \quad \text{ and } \quad
 \svdMax{\LocalModel[\rightAdjacent(\omega)]{\Delta}(\omega)}
\end{equation*}
In view of obtaining the maximum singular value, these are `interpolated' to obtain a single estimate:
\begin{equation}
  \svdMax{\Delta_{\LMM}(\omega)}
    \isdef
    \max \Set{
       \svdMax{\LocalModel[\leftAdjacent(\omega)]{\Delta}(\omega)},
        \svdMax{\LocalModel[\rightAdjacent(\omega)]{\Delta}(\omega)}
    }
    \label{eq:lrmhinf:DeltaLRMInterpolation}
\end{equation}
by retaining the largest of both.
%TODO: remark that this notation is deceiving: there is no $\Delta_{\LMM}$, and hence, its Hinf norm does not exist. Both notations are just to indicate
It follows that
\begin{align}
  \widehat{\infnorm{\Delta_{\LMM}}}
    & \isdef
    \sup_{\omega\in\Omega}
    \svdMax{\Delta_{\LMM}(\omega)} \\
   &  =
      \sup_{\omega\in\Omega} \; 
      \max \Set{
                 \svdMax{\LocalModel[\leftAdjacent(\omega)]{\Delta}(\omega)}, 
                 \svdMax{\LocalModel[\rightAdjacent(\omega)]{\Delta}(\omega)}}
  \label{eq:lrmhinf:gammaInterpolOptim}
  \text{.}
\end{align}

@@

>>>>

\paragraph{Interpolation method}
To allow inspection of $\svdMax{\Delta(\omega)}$ in~\eqref{eq:lrmhinf:HinfNormSISO} for arbitrary values of $\omega \in \Omega$, we propose an interpolation approach to estimate $\gamma$ and to allow visual inspection of $\svdMax{\Delta(\omega)}$.
It can be understood intuitively that due to the limited validity domain of the local models, an estimate of $\Delta(\omega)$ can only be obtained from $\LocalModel[k(\omega)]{\Delta}$ when the distance $\abs{\omega_k-\omega}$ is small.
As the local models are each constructed around the frequency $\omega_k$, for an arbitrary $\omega \in \Omega$, one can find two adjacent frequencies around which such local models are available.
To this end, two functions that indicate respectively the left and the right adjacent local models for frequency $\omega \in \Omega$ are defined:
\begin{align}
  \leftAdjacent(\omega) & 
                \isdef
                  \max
                  \Set{
                    k 
                    |
                      \omega_k \in \DFTGrid,  \omega_k \leq \omega
                  }\\
  \rightAdjacent(\omega) & 
                \isdef
                  \min
                  \Set{
                    k
                    |
                      \omega_k \in \DFTGrid,  \omega_k \geq \omega
                  }
  \text{.}
  \label{eq:lrmhinf:kL-kR-indexing-functions}
\end{align}
Using the $\leftAdjacent(\omega)$ and $\rightAdjacent(\omega)$ functions, two candidate values for $\svdMax{\Delta(\omega)}$ are obtained:
\begin{equation*}
 \svdMax{\LocalModel[\leftAdjacent(\omega)]{\Delta}(\omega)} 
 \quad \text{ and } \quad
 \svdMax{\LocalModel[\rightAdjacent(\omega)]{\Delta}(\omega)}
\end{equation*}
In view of obtaining the maximum singular value, these are `interpolated' to obtain a single estimate:
\begin{equation}
  \svdMax{\Delta_{\LMM}(\omega)}
    \isdef
    \max \Set{
       \svdMax{\LocalModel[\leftAdjacent(\omega)]{\Delta}(\omega)},
        \svdMax{\LocalModel[\rightAdjacent(\omega)]{\Delta}(\omega)}
    }
    \label{eq:lrmhinf:DeltaLRMInterpolation}
\end{equation}
by retaining the largest of both.
It follows that
\begin{align}
  \widehat{\phantom{_\infty}\infnorm{\Delta_{\LMM}}}
    & \isdef
    \sup_{\omega\in\Omega}
    \svdMax{\Delta_{\LMM}(\omega)} \\
   &  =
      \sup_{\omega\in\Omega} \; 
      \max \Set{
                 \svdMax{\LocalModel[\leftAdjacent(\omega)]{\Delta}(\omega)}, 
                 \svdMax{\LocalModel[\rightAdjacent(\omega)]{\Delta}(\omega)}}
  \label{eq:lrmhinf:gammaInterpolOptim}
  \text{.}
\end{align}

@@

\begin{remark}
The notions $\svdMax{\Delta_{\LMM}(\omega)}$ and the ensuing  $\widehat{\phantom{_\infty}\infnorm{\Delta_{\LMM}}}$  should be regarded as notational convenience to denote that local models are used to estimate the maximal singular value and $\Hinf{}$ norm, respectively.
In reality, there is no tangible `$\Delta_{\LMM}$' that is constructed: neighboring local models are stitched together using the `$\max$' operator.
\end{remark}
